Evaluation of Types

### 2020-05-15 evaluation/R/evaluate-type-analysis.Rmd

---
title: Evaluation of Types
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
params:
  type_analysis_datafile: ../data/type-analysis/merged/merged.csv
  graph_dirpath: ../../paper/plots/
  table_dirpath: ../../paper/tables/
---

@@

@@

union_types <-
union_data %>%
group_by(package_name, function_name, parameter_position, alternative_count) %>%
summarize(kind = paste0(sort(kind), collapse=" | ")) %>%
ungroup() %>%
group_by(alternative_count, kind) %>%
summarize(count = n()) %>%
ungroup() %>%
group_by(alternative_count) %>%
arrange(desc(count)) %>%
ungroup() %>%
group_by(alternative_count) %>%
mutate(percentage = round(100 * count / sum(count), 2),
       cumsum_percentage = round(100 * cumsum(count) / sum(count), 2)) %>%
ungroup() %>%
group_by(alternative_count) %>%
slice(1:20) %>%
ungroup()

>>>>

---
title: Evaluation of Types
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
params:
  type_analysis_datafile: ../data/type-analysis/merged/merged.csv
  graph_dirpath: ../../paper/plots/
  table_dirpath: ../../paper/tables/
  macro_dirpath: ../../paper/macros/
---

@@

macro_filename <- file.path(params$macro_dirpath, "macros.tex")

@@

generate_macro("PercUnitypedPositions", 
               union_frequency_folded %>% filter(alternative_count == "1") %>% pull(percentage),
               macro_filename)

generate_macro("PercManytypedPositions", 
               union_frequency_folded %>% filter(alternative_count == "> 3") %>% pull(percentage),
               macro_filename)

union_types <-
union_data %>%
group_by(package_name, function_name, parameter_position, alternative_count) %>%
summarize(kind = paste0(sort(kind), collapse=" | ")) %>%
ungroup() %>%
group_by(alternative_count, kind) %>%
summarize(count = n()) %>%
ungroup() %>%
group_by(alternative_count) %>%
arrange(desc(count)) %>%
ungroup() %>%
group_by(alternative_count) %>%
mutate(percentage = round(100 * count / sum(count), 1),
       cumsum_percentage = round(100 * cumsum(count) / sum(count), 1)) %>%
ungroup() %>%
group_by(alternative_count) %>%
slice(1:20) %>%
ungroup()
